The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-03-28 doc/paper/skysubtraction.tex
another small update

A 2-step iterative procedure is loop through
a range of possible polynomial

>>>>

We apply the best guess coefficients to predict the approximate pixel 
positions of the suitable list of arc lines.  The arc line centroids
are traced across extracted spectra (along the axis of 320 fibers).
The centroids are fit to a smooth polynomial as a function of fiber
position on the arc-lamp image, and subsequently fit through 6 iterations
with simple flux weighting to arrive at a converged measure of line 
centroids in each extracted spectrum.  Lines are excluded from the resulting
list if the flux-weighted centroids are bad in more than 10\% of the
spectra or if the RMS residuals are larger than 20\% of a pixel.
We perform an iterative 4th order Legendre polynomial fit of 
logarithmic wavelength as a function of pixel in each spectrum, 
and retain a list of rejected centroids, 
which have deviations relative to the model of
10\% of a pixel width.  An additional requirement is applied to each
suitable arc line, wherein the line is rejected in no more than 3 fibers
per bundle of 20.  Rejected centroids are replaced with the appropriate
positions based on a linear interpolation of the differences of non-masked
centroids relative to updated polynomial fits per spectrum.
The final set of positions, where the same number of line positions have
reliable centroids per spectrum, are fit to produce the final wavelength
coefficients which give the logarithmic (base 10) wavelengths as a function
of spectral pixel.

An arc-lamp image is declared bad using the first 4 tests as employed
in tests of the flat-field images.  In addition, an arc-lamp exposure
is declared unacceptable ("BAD") if any of these following criteria are met:
5) All 8 arc-lamps must be on, 4 Neon lamps and 5 Mercury-Cadmium lamps,
6) The initial cross-correlation coefficient is less than 0.5,
7) Less than 6 arc lines are acceptable after quality assurance checks.

The width of unblended arc lines are determined as an average over
each bundle of 20 spectra.  In short, the arc-lamp emission lines 
are extracted (with a Gaussian spectral profile) 
allowing free parameters for the area and width of each suitable line.
The resulting Gaussian widths per fiber bundle are fit 
with a low order polynomial as a function of average line position
(the fit is quadratic and cubic for the blue and red side respectively).
The fitted quantity is misnomerly (sp?) referred to as the arc-lamp dispersion,
although the values reflect the standard deviation of a Gaussian spectral
profile in pixel units.

(or just refer to data model appendix instead of the paragraph below:)

The arc-lamp reductions are written to disk at this stage, and
stored in an extended FITS file:  HDU #0 contains the processed
and extracted arc-lamp spectra as counts per pixel, HDU #1 contains
the identified arc line wavelengths and the measured line centroids
(including replaced positions of rejections), HDU #2 contains a single
structure with the Legendre polynomial coefficients applicable to each
of the 320 arc-lamp spectra, HDU #3 contains the maskbits for each spectrum,
and HDU #4 contains the polynomial coefficients to describe the arc-lamp
Gaussian widths as a function of spectral pixel.
